From Education to Entrepreneurship

### 2014-12-07 index.Rmd
Updated the branch README and fixed spelling errors

pkgs <- c('repmis', 'ggvis', 'devtools', 'googleVis', 'countrycode', 'reshape2', 'shiny',
          'httpuv', 'Zelig', 'stargazer', 'Amelia')
repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')

@@

# Dropp X column
CD$X <- NULL

>>>>

# Create a vector of packages used
pkgs <- c('repmis', 'ggvis', 'devtools', 'googleVis', 'countrycode', 'reshape2', 'shiny', 'httpuv', 'Zelig',
          'stargazer', 'Amelia')

# Create citations txt file
repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')

@@

# Drop X column
CD$X <- NULL
